---
title: "Using R in Power BI"
author: "Sudarshana A"
date: "August 11, 2020"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: 3
---


## Prerequisite

* R must be installed on the same Windows computer as Power BI Desktop

https://www.r-project.org/

Australia - mirrors

|||
|---|---|
| https://cran.csiro.au/	| CSIRO |
| https://mirror.aarnet.edu.au/pub/CRAN/	| AARNET |
| https://cran.ms.unimelb.edu.au/	| School of Mathematics and Statistics, University of Melbourne |
| https://cran.curtin.edu.au/	| Curtin University |


</br>

* Good to have

IDE to use with R, Notepad++, R Studio, VS etc.



## Import Data

To import data you need to create a dataframe. Power BI can access the dataframes and you can select required dataframes to import.

* Connect to available dataset in R
* import csv, xlsx, sql etc. data to R then connect
* import data to R, transform, clean up data and then connect


### Example 1 - Connect to available dataset in R

We can use available dataset in R and import this to Power BI

`cars` dataset in R consist of breaking distances vs. speed data.

we can preview the data using `head()` function.


```{r}
head(cars)

```

Lets import this dataset to Power BI by assigning to a dataframe.

In **Power BI**, click *Get Data -> Other -> R script*


Use the following R script to get the data from *cars* dataset.

```{r}
cars_data <- cars

```





## Tranform Data

## Visualisations


